Data for ms. 1

### 2017-05-02 ms1/ms1.Rmd
ignore feather

  pde = read_tsv(sprintf('../pde_%i.tsv', year))

@@

big_model = data_by_field('big_model') %>%
  mutate(term=stringr::str_replace(term, 'TRUE$', '')) %>%
  left_join(rename(condition_names, term=condition, condition=condition_name), by='term') %>%
  filter(term != '(Intercept)') %>%
  mutate(term=if_else(is.na(condition), term, condition)) %>%
  select(year, term, estimate, std.error) %T>%
  write_tsv('tables/tmp_big_model.tsv')
```

@@

>>>>

  pde = read_tsv(sprintf('../pde_%i.tsv', year)) %>%
    filter(bene_id %in% bene$bene_id)

@@

add_ci = function(df) mutate(df, ci=1.96*std.error, cil=estimate-ci, ciu=estimate+ci)

big_model = data_by_field('big_model') %>%
  mutate(term=stringr::str_replace(term, 'TRUE$', '')) %>%
  left_join(rename(condition_names, term=condition, condition=condition_name), by='term') %>%
  filter(term != '(Intercept)') %>%
  mutate(term=if_else(is.na(condition), term, condition)) %>%
  mutate(adj.p=p.adjust(p.value, method='BH')) %>%
  select(year, term, estimate, std.error, adj.p) %T>%
  write_tsv('tables/tmp_big_model.tsv') %>%
  add_ci() %>%
  filter(year==2011) %>%
  select(-year, -ci) %>%
  arrange(desc(estimate)) %>%
  kable
```

# Abstract's linear model results

```{r ci}
extract_ci = function(y) {
  f = formula(paste0(y, ' ~ age'))
  claims_by_age %>%
    filter(group=='all') %>%
    lm(f, data=.) %>%
    tidy %>%
    filter(term=='age') %>%
    add_ci() %>%
    mutate(model=y) %>%
    select(model, estimate, cil, ciu) %>%
    mutate_if(is.numeric, function(x) round(x, digits=4))
}

bind_rows(lapply(c('mean_n_claims', 'mean_n_cc', 'mean_n_visits'), extract_ci)) %>% kable
```

@@

`r big_model`
